---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Poppins:ital,wght@0,100;0,200;0,300;0,400;0,500;0,600;0,700;0,800;0,900;1,100;1,200;1,300;1,400;1,500;1,600;1,700;1,800;1,900&display=swap');

* {
  background: #adf7fc;
  margin: 10px;
}

h2 {
  font-family: "Poppins", sans-serif;
  font-weight: 500;
  font-style: normal;
  text-align: center;
}

h3 {
  font-family: "Poppins", sans-serif;
  font-weight: 300;
  font-style: normal;
  text-align: center;
}

p {
  text-align: left;
  font-family: "Poppins", sans-serif;
}
```

## Youtube viewer preference & behaviour

### This form is intended to study users behaviour when interacting with youtube videos, and what factors would influence their video preferences.

In this report, I will mainly focus on exploring peoples behaviour and preference while browsing and watching youtube videos

Firstly, let's load some necessary packages to get us started:
```{r echo = T, results='hide'}
library(tidyverse)
library(magick)
```

Load the csv file, and assign it to an object called logged_data:
```{r echo = T, results='hide'}

csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQpMQvmWiKBQwIKecKDuRBZyhaHCpfOw-0hyIHEuD849GazihA4DT1w0W_WCc_Y3hsojdDaNbd6mJpW/pub?gid=1765259499&single=true&output=csv"

logged_data <- read_csv(csv_file)

```

Rename the object *logged_data* to *latest_data* and rename the columns:
```{r echo = T, results='hide'}

latest_data <- logged_data %>%
  rename(video_categories = 2,
         total_time_per_day = 3,
         factors = 4,
         experience = 5,
         rating = 6)

glimpse(latest_data)
```

Now since we have loaded all the data and created the data frame successfully. Let's start exploring by looking at the most popular video category people have chosen:
So in the survey, I listed 16 different categories that I believe are some of the most popular ones, and we will pick the most popular one out of these 16 categories.

And the R code snippet is as follows:

```{r echo = T, results='hide'}

most_popular_category <- latest_data %>%
  count(video_categories, sort = TRUE) %>%  # Count occurrences and sort in descending order
  slice(1)  # Get the top category
most_popular_category
```

The result we got after running the code above is "sport", which means the sport is the most popular category people like to watch

The second one is about what would people rate about their experience on youtube out of 10

Here's the R code snippet:

```{r echo = T, results='hide'}

ratings <- latest_data %>%
  select(rating)
highest_rating <- max(ratings)
highest_rating
```

The result is 10, which means most people who took part of this survey are very satisfied with the service that youtube is currenty providing.

Let's then look at some bar charts

So the first bar chart is about the most popular category of course. After briefly touched on this topic previously, let's now make a bar chart about it so that we can better visualize the data!!!

```{r}
#plot no.1 x = video_categories
ggplot(data = latest_data) +
  geom_bar(aes(x = video_categories))
```

And the second bar chart is about the total time the partcipants usually spend on youtube:
```{r}
#plot no.2 x = total_time_spent_daily
ggplot(data = latest_data) +
  geom_bar(aes(x = total_time_per_day))
```


